Data analysis to support temporary cycleways

### 2020-05-08 README.Rmd
Add article

rmarkdown::render("london.Rmd") # check
rmarkdown_files = paste0(tolower(las_top$name), ".Rmd")
lapply(rmarkdown_files, rmarkdown::render)
webshot::install_phantomjs()
# general analysis of data
# piggyback::pb_download("rsf.Rds", "cyipt/cyipt-phase-1-data")
rsf = readRDS("rsf.Rds")
names(rsf)
rtid = readr::read_csv("~/cyipt/cyipt-server-data/malcolm/roadtypes.csv")
rsf = left_join(rsf, rtid)
rsf_spare_lane = rsf %>% filter(
  (lanespsvforward + lanesforward) > 1 |
    (lanespsvbackward + lanesbackward) > 1,
  !grepl(pattern = "motorway", highway)
)
saveRDS(rsf_spare_lane, "rsf_spare_line.Rds")
# piggyback::pb_upload("rsf_spare_line.Rds", "cyipt/cyipt-phase-1-data")

>>>>

rmarkdown::render("london.Rmd") # check
rmarkdown_files = paste0(tolower(las_top$name), ".Rmd")
lapply(rmarkdown_files, rmarkdown::render)
webshot::install_phantomjs()
# general analysis of data
# piggyback::pb_download("rsf.Rds", "cyipt/cyipt-phase-1-data")
rsf = readRDS("rsf.Rds")
names(rsf)
rtid = readr::read_csv("~/cyipt/cyipt-server-data/malcolm/roadtypes.csv")
readr::write_csv(rtid, "rtid.csv")
piggyback::pb_upload("rtid.csv")
rsf = left_join(rsf, rtid)
rsf_spare_lane = rsf %>% filter(
  (lanespsvforward + lanesforward) > 1 |
    (lanespsvbackward + lanesbackward) > 1,
  !grepl(pattern = "motorway", highway)
)
saveRDS(rsf_spare_lane, "rsf_spare_line.Rds")
# piggyback::pb_upload("rsf_spare_line.Rds", "cyipt/cyipt-phase-1-data")
